Evaluating procedures for updating catch advice between stock assessments of reef fishes with management strategy evaluation

### 2022-06-02 RunMSE/SEFSC/Manuscript/MainText.tex
move large files out of repo

\begin{abstract}
We built operating models for three reef fish species from the US Southeast Atlantic, based on recent stock assessments. We developed 10 scenerios and 13 management procedures. Management procedures varied in terms of how often stock assessments were conducted, and how catch advice was adjusted between stock assessments.

@@

%% TABLES
\newpage
\section*{Tables}

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in,height=7in]{../Figs/AddInd.pdf}
\end{center}
\begin{flushleft}
\caption{Indices derived from BAM stock assessments available during the projection period, for the SCA\_5 MP in the Base scenario. Shaded areas represent 95\% CI for indices among simulation runs.}
\label{fig:phasePlot1}
\end{flushleft}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in,height=7in]{../Figs/phasePlot1.pdf}
\end{center}
\begin{flushleft}
\caption{Phase plots for the base scenario and the first set of experimental scenarios}
\label{fig:phasePlot1}
\end{flushleft}
\end{figure}

% \begin{figure}[!ht]
% \begin{center}
% \includegraphics[width=6in,height=7in]{../Figs/phasePlot2.pdf}
% \end{center}
% \begin{flushleft}
% \caption{Phase plots for the base scenario and the second set of experimental scenarios}
% \label{fig:phasePlot2}
% \end{flushleft}
% \end{figure}

%% APPENDIX
% \begin{appendix}
%
% \clearpage
% \section*{Appendix S1}
%
% \setcounter{table}{0}
% \renewcommand{\thetable}{S\arabic{table}}
%
% \input{../Results/Appendix.tex}
%
% \input{../Results/biodivByBlock.tex}
%
% \end{appendix}

>>>>

\begin{abstract}
We conducted a management strategy evaluation (MSE) to investigate how management procedures that adjust catch advice between stock assessments performed compared with existing management procedures. We built operating models (OM) for four reef fish species from the US Southeast Atlantic, based on recent stock assessments including Black Sea Bass, Red Porgy, Snowy Grouper, and Vermilion Snapper. These OM contained parameters and data specific to each stock, associated fisheries, and the sampling programs that monitor them. The analysis assumed efficient implementation of management, such that observed catch was equal to total allowable catch (TAC). Our analysis focused on a base scenario intended to most closely characterize the reality of each stock. We also developed multiple alternative scenarios to investigate the sensitivity of the analysis to deviations from the base configuration. A set of management procedures (MP) was applied independently in closed loop simulation for each species and scenario, with many replicate runs. The MP varied in terms of how often stock assessments were conducted (every 1, 5, or 10 years), and how catch advice (i.e. TAC) was adjusted between stock assessments. Between assessments, TACs were either fixed, adjusted based on projections, or adjusted based on a reference index of abundance. Results varied among species and scenarios, but generally showed that healthy stock and fishery status ($\mathrm{SSB>SSB_{MSY}}$ and $F<F_{\mathrm{MSY}}$) and comparable levels of total catch could be maintained with stock assessments conducted every 1, 5 or 10 years, whether TACs were fixed, projected, or adjusted based on indices of abundance. But these management procedures vary in terms of average annual variability in yield (AAVY) which was highest when TACs were adjusted based on indices of abundance and lowest when TACs were fixed between assessments.

@@

%% TABLES
% \newpage
% \section*{Tables}

@@

% Indices
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in,height=5.25in]{../Figs/MSEDiagram.png}
\end{center}
\begin{flushleft}
\caption{Diagram of the MSE process. The operating model is the simulated "true" dynamics of the system; the observation, or data-generating, model simulates the process of scientific data collection from the stock and fishery; the estimating model is used to estimate the status of the stock; the catch control rule is a pre-defined decision rule that adaptively adjusts management measures based on the status of the stock; the implementation model implements the management recommendations from the catch control rule back into the operating model with implementation and management uncertainty. Note that all model components highlighted in gray comprise the management procedure and performance metrics (or management procedure performance) is measured from the operating model.}
\label{fig:diagram}
\end{flushleft}
\end{figure}

% Indices
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in,height=7in]{../Figs/AddInd.pdf}
\end{center}
\begin{flushleft}
\caption{Indices derived from BAM stock assessments available during the projection period, for the SCA (10) MP in the Base scenario, where stock assessments are conducted every 10 years during the projection period (dashed vertical lines). Shaded areas represent 95\% CI for indices among simulation runs.}
\label{fig:AddInd}
\end{flushleft}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in, height=7in]{../Figs/boxplotSBSBMSY1.pdf}
\end{center}
\begin{flushleft}
\caption{Box plots of $\mathrm{SSB/SSB_{MSY}}$ for the base scenario. Grouped boxes represent sequential time periods during the projection period. Boxes represent interquartile range (IQR). Whiskers are drawn to $1.5\times\mathrm{IQR}$.}
\label{fig:boxplotSBSBMSY1}
\end{flushleft}
\end{figure}
\clearpage\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in, height=7in]{../Figs/boxplotFFMSY1.pdf}
\end{center}
\begin{flushleft}
\caption{Box plots of $\mathrm{F/F_{MSY}}$ for the base scenario. Grouped boxes represent sequential time periods during the projection period. Boxes represent interquartile range (IQR). Whiskers are drawn to $1.5\times\mathrm{IQR}$.}
\label{fig:boxplotFFMSY1}
\end{flushleft}
\end{figure}
\clearpage\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in, height=7in]{../Figs/boxplotCatchTotal1.pdf}
\end{center}
\begin{flushleft}
\caption{Box plots of total catch (annual catches summed across each time period) for the base scenario. Grouped boxes represent sequential time periods during the projection period. Boxes represent interquartile range (IQR). Whiskers are drawn to $1.5\times\mathrm{IQR}$.}
\label{fig:boxplotCatchTotal1}
\end{flushleft}
\end{figure}
\clearpage\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in, height=7in]{../Figs/boxplotAAVY1.pdf}
\end{center}
\begin{flushleft}
\caption{Box plots of average annual variation in yield ($\mathrm{AAVY}$) for the base scenario. Grouped boxes represent sequential time periods during the projection period. Boxes represent interquartile range (IQR). Whiskers are drawn to $1.5\times\mathrm{IQR}$.}
\label{fig:boxplotAAVY1}
\end{flushleft}
\end{figure}
\clearpage
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in, height=7in]{../Figs/tsCatchMSY1.pdf}
\end{center}
\begin{flushleft}
\caption{Time series of median $\mathrm{catch/MSY}$ among simulation runs for the base scenario.Vertical dotted lines indicate assessment years at 10 yr intervals.}
\label{fig:tsCatchMSY1}
\end{flushleft}
\end{figure}
\clearpage\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in, height=7in]{../Figs/tsCatchMSY1B.pdf}
\end{center}
\begin{flushleft}
\caption{Time series of median $\mathrm{catch/MSY}$ among simulation runs for the base scenario.Vertical dotted lines indicate assessment years at 5 yr intervals.}
\label{fig:tsCatchMSY1B}
\end{flushleft}
\end{figure}
\clearpage\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in, height=7in]{../Figs/tsFFmsy1.pdf}
\end{center}
\begin{flushleft}
\caption{Time series of median $\mathrm{F/F_{MSY}}$ among simulation runs for the base scenario.Vertical dotted lines indicate assessment years at 10 yr intervals.}
\label{fig:tsFFmsy1}
\end{flushleft}
\end{figure}
\clearpage\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in, height=7in]{../Figs/tsFFmsy1B.pdf}
\end{center}
\begin{flushleft}
\caption{Time series of median $\mathrm{F/F_{MSY}}$ among simulation runs for the base scenario.Vertical dotted lines indicate assessment years at 5 yr intervals.}
\label{fig:tsFFmsy1B}
\end{flushleft}
\end{figure}
\clearpage\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in, height=7in]{../Figs/tsSSBSSBmsy1.pdf}
\end{center}
\begin{flushleft}
\caption{Time series of median $\mathrm{SSB/SSB_{MSY}}$ among simulation runs for the base scenario.Vertical dotted lines indicate assessment years at 10 yr intervals.}
\label{fig:tsSSBSSBmsy1}
\end{flushleft}
\end{figure}
\clearpage\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in, height=7in]{../Figs/tsSSBSSBmsy1B.pdf}
\end{center}
\begin{flushleft}
\caption{Time series of median $\mathrm{SSB/SSB_{MSY}}$ among simulation runs for the base scenario.Vertical dotted lines indicate assessment years at 5 yr intervals.}
\label{fig:tsSSBSSBmsy1B}
\end{flushleft}
\end{figure}
\clearpage

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=7in, height=3.5in]{../Figs/trAAVYP1001.pdf}
\end{center}
\begin{flushleft}
\caption{Trade off plots of the probability that average annual variability in yield (AAVY) <20\%, versus  the probability that $\mathrm{SSB > SSB_{MSY}}$ among simulation runs for the base scenario. Plots are based on data for the last 10 years of the projection period.}
\label{fig:trAAVYP1001}
\end{flushleft}
\end{figure}
\clearpage\begin{figure}[!ht]
\begin{center}
\includegraphics[width=7in, height=3.5in]{../Figs/trAAVYPNOF1.pdf}
\end{center}
\begin{flushleft}
\caption{Trade off plots of the probability that average annual variability in yield (AAVY) <20\%, versus  the probability that $\mathrm{F < F_{MSY}}$ among simulation runs for the base scenario. Plots are based on data for the last 10 years of the projection period.}
\label{fig:trAAVYPNOF1}
\end{flushleft}
\end{figure}
\clearpage\begin{figure}[!ht]
\begin{center}
\includegraphics[width=7in, height=3.5in]{../Figs/trAAVYYldLT1.pdf}
\end{center}
\begin{flushleft}
\caption{Trade off plots of the probability that average annual variability in yield (AAVY) <20\%, versus  longterm yield among simulation runs for the base scenario. Plots are based on data for the last 10 years of the projection period.}
\label{fig:trAAVYYldLT1}
\end{flushleft}
\end{figure}
\clearpage\begin{figure}[!ht]
\begin{center}
\includegraphics[width=7in, height=3.5in]{../Figs/trP100YldLT1.pdf}
\end{center}
\begin{flushleft}
\caption{Trade off plots of the probability that $\mathrm{SSB > SSB_{MSY}}$ versus  longterm yield among simulation runs for the base scenario. Plots are based on data for the last 10 years of the projection period.}
\label{fig:trP100YldLT1}
\end{flushleft}
\end{figure}
\clearpage\begin{figure}[!ht]
\begin{center}
\includegraphics[width=7in, height=3.5in]{../Figs/trPNOFP1001.pdf}
\end{center}
\begin{flushleft}
\caption{Trade off plots of the probability that $\mathrm{F < F_{MSY}}$  versus  the probability that $\mathrm{SSB > SSB_{MSY}}$ among simulation runs for the base scenario. Plots are based on data for the last 10 years of the projection period.}
\label{fig:trPNOFP1001}
\end{flushleft}
\end{figure}
\clearpage
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=7in, height=3.5in]{../Figs/phasePlot1.pdf}
\end{center}
\begin{flushleft}
\caption{Phase plots of the probability that $\mathrm{F > F_{MSY}}$  versus  the probability that $\mathrm{SSB > SSB_{MSY}}$ among simulation runs for the base scenario.}
\label{fig:phasePlot1}
\end{flushleft}
\end{figure}
\clearpage
%% APPENDIX
\begin{appendix}

\clearpage
\section*{Appendix}

\setcounter{figure}{0}
\renewcommand{\thefigure}{S\arabic{figure}}

% \setcounter{table}{0}
% \renewcommand{\thetable}{S\arabic{table}}
%
% \input{../Results/Appendix.tex}
%
% \input{../Results/biodivByBlock.tex}
%

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in, height=7in]{../Figs/boxplotSBSBMSY2.pdf}
\end{center}
\begin{flushleft}
\caption{Box plots of $\mathrm{SSB/SSB_{MSY}}$ for the base and alternative scenarios. Grouped boxes represent sequential time periods during the projection period. Boxes represent interquartile range (IQR). Whiskers are drawn to $1.5\times\mathrm{IQR}$.}
\label{fig:boxplotSBSBMSY2}
\end{flushleft}
\end{figure}
\clearpage\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in, height=7in]{../Figs/boxplotFFMSY2.pdf}
\end{center}
\begin{flushleft}
\caption{Box plots of $\mathrm{F/F_{MSY}}$ for the base and alternative scenarios. Grouped boxes represent sequential time periods during the projection period. Boxes represent interquartile range (IQR). Whiskers are drawn to $1.5\times\mathrm{IQR}$.}
\label{fig:boxplotFFMSY2}
\end{flushleft}
\end{figure}
\clearpage\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in, height=7in]{../Figs/boxplotCatchTotal2.pdf}
\end{center}
\begin{flushleft}
\caption{Box plots of total catch (annual catches summed across each time period) for the base and alternative scenarios. Grouped boxes represent sequential time periods during the projection period. Boxes represent interquartile range (IQR). Whiskers are drawn to $1.5\times\mathrm{IQR}$.}
\label{fig:boxplotCatchTotal2}
\end{flushleft}
\end{figure}
\clearpage\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in, height=7in]{../Figs/boxplotAAVY2.pdf}
\end{center}
\begin{flushleft}
\caption{Box plots of average annual variation in yield ($\mathrm{AAVY}$) for the base and alternative scenarios. Grouped boxes represent sequential time periods during the projection period. Boxes represent interquartile range (IQR). Whiskers are drawn to $1.5\times\mathrm{IQR}$.}
\label{fig:boxplotAAVY2}
\end{flushleft}
\end{figure}
\clearpage
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in, height=7in]{../Figs/tsCatchMSY2.pdf}
\end{center}
\begin{flushleft}
\caption{Time series of median $\mathrm{catch/MSY}$ among simulation runs for the base scenario.Vertical dotted lines indicate assessment years at 10 yr intervals.}
\label{fig:tsCatchMSY2}
\end{flushleft}
\end{figure}
\clearpage\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in, height=7in]{../Figs/tsCatchMSY2B.pdf}
\end{center}
\begin{flushleft}
\caption{Time series of median $\mathrm{catch/MSY}$ among simulation runs for the base scenario.Vertical dotted lines indicate assessment years at 5 yr intervals.}
\label{fig:tsCatchMSY2B}
\end{flushleft}
\end{figure}
\clearpage\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in, height=7in]{../Figs/tsFFmsy2.pdf}
\end{center}
\begin{flushleft}
\caption{Time series of median $\mathrm{F/F_{MSY}}$ among simulation runs for the base scenario.Vertical dotted lines indicate assessment years at 10 yr intervals.}
\label{fig:tsFFmsy2}
\end{flushleft}
\end{figure}
\clearpage\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in, height=7in]{../Figs/tsFFmsy2B.pdf}
\end{center}
\begin{flushleft}
\caption{Time series of median $\mathrm{F/F_{MSY}}$ among simulation runs for the base scenario.Vertical dotted lines indicate assessment years at 5 yr intervals.}
\label{fig:tsFFmsy2B}
\end{flushleft}
\end{figure}
\clearpage\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in, height=7in]{../Figs/tsSSBSSBmsy2.pdf}
\end{center}
\begin{flushleft}
\caption{Time series of median $\mathrm{SSB/SSB_{MSY}}$ among simulation runs for the base scenario.Vertical dotted lines indicate assessment years at 10 yr intervals.}
\label{fig:tsSSBSSBmsy2}
\end{flushleft}
\end{figure}
\clearpage\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in, height=7in]{../Figs/tsSSBSSBmsy2B.pdf}
\end{center}
\begin{flushleft}
\caption{Time series of median $\mathrm{SSB/SSB_{MSY}}$ among simulation runs for the base scenario.Vertical dotted lines indicate assessment years at 5 yr intervals.}
\label{fig:tsSSBSSBmsy2B}
\end{flushleft}
\end{figure}
\clearpage
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=7in, height=8in]{../Figs/trAAVYP1002.pdf}
\end{center}
\begin{flushleft}
\caption{Trade off plots of the probability that average annual variability in yield (AAVY) <20\%, versus  the probability that $\mathrm{SSB > SSB_{MSY}}$ among simulation runs for the base and alternative scenarios. Plots are based on data for the last 10 years of the projection period.}
\label{fig:trAAVYP1002}
\end{flushleft}
\end{figure}
\clearpage\begin{figure}[!ht]
\begin{center}
\includegraphics[width=7in, height=8in]{../Figs/trAAVYPNOF2.pdf}
\end{center}
\begin{flushleft}
\caption{Trade off plots of the probability that average annual variability in yield (AAVY) <20\%, versus  the probability that $\mathrm{F > F_{MSY}}$ among simulation runs for the base and alternative scenarios. Plots are based on data for the last 10 years of the projection period.}
\label{fig:trAAVYPNOF2}
\end{flushleft}
\end{figure}
\clearpage\begin{figure}[!ht]
\begin{center}
\includegraphics[width=7in, height=8in]{../Figs/trAAVYYldLT2.pdf}
\end{center}
\begin{flushleft}
\caption{Trade off plots of the probability that average annual variability in yield (AAVY) <20\%, versus  longterm yield among simulation runs for the base and alternative scenarios. Plots are based on data for the last 10 years of the projection period.}
\label{fig:trAAVYYldLT2}
\end{flushleft}
\end{figure}
\clearpage\begin{figure}[!ht]
\begin{center}
\includegraphics[width=7in, height=8in]{../Figs/trPNOFP1002.pdf}
\end{center}
\begin{flushleft}
\caption{Trade off plots of the probability that $\mathrm{F > F_{MSY}}$  versus  the probability that $\mathrm{SSB > SSB_{MSY}}$ among simulation runs for the base and alternative scenarios. Plots are based on data for the last 10 years of the projection period.}
\label{fig:trPNOFP1002}
\end{flushleft}
\end{figure}
\clearpage
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=7in, height=8in]{../Figs/phasePlot2.pdf}
\end{center}
\begin{flushleft}
\caption{Phase plots of the probability that $\mathrm{F > F_{MSY}}$  versus  the probability that $\mathrm{SSB > SSB_{MSY}}$ among simulation runs for the base and alternative scenarios.}
\label{fig:phasePlot2}
\end{flushleft}
\end{figure}
\clearpage

\end{appendix}
